\documentclass[]{gagan-resume}


\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LAST UPDATED DATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Gagan Sikri}{ 
\href{mailto:me@gagansikri.com}{me@gagansikri.com} | 
 +91-99915-59940}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep}
\section{Skills}
\subsection{Programming}
JavaScript, jQuery, React, VueJS, HTML5, CSS3, PHP
 \\
\subsection{Database}
MySQL, PostgreSQL, NoSQL, MongoDB, TaffyDB
 \\
\subsection{Tools}
VSCode, Webstorm, NPM, Gulp, Webpack, Enzyme, Git, Postman, JIRA, Trello
 \\
\subsection{Experience With}
Data Visualization, UX Enhancement, App Architecture, Web Performance \& Design Patterns
 \\
\subsection{Design}
Sketch
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Kurukshetra University}
\descript{B.Tech - Computer Science}
\location{2011 - 2015 | Kurukshetra, Haryana, IN \\ Cum. Percentage: 72.5\%}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/sikrigagan}{\custombold{sikrigagan}} \\
Twitter://  \href{https://twitter.com/sikrigagan}{\custombold{@sikrigagan}} \\
Linkedin://  \href{https://linkedin.com/in/sikrigagan}{\custombold{@sikrigagan}} \\
Stack Overflow://  \href{https://stackoverflow.com/users/4129965/sikrigagan}{\custombold{sikrigagan}} \\
Facebook://  \href{https://facebook.com/sikrigagan}{\custombold{sikrigagan}}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WRITING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Writing} 
\textbf{\href{https://scotch.io/@sikrigagan}{Scotch.io (2)}}\\
\textbf{\href{https://dzone.com/users/2733735/sikrigagan.html}{DZone (6)}}\\
\textbf{\href{https://tutsplus.com/authors/gagan-sikri}{Envato tuts+ (1)}}\\
\textbf{\href{https://www.codementor.io/sikrigagan}{Codementor (1)}}\\
\textbf{\href{http://www.c-sharpcorner.com/members/gagan-sikri}{C\# Corner (11)}}\\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth}

\vspace{\topsep}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\runsubsection{Software Engineer}
\descript{| FusionCharts }
\location{August 2018 - Present | Bangalore, Karnataka, IN}
\vspace{\topsep}
\vspace{\topsep}
\begin{tightemize}
\item Part of Dev-X team responsible for handling the complete web architecture for FusionCharts. Also involved in design reviews and provide inputs to design recommendations.
\item Handling DaaS team to implement custom dashboard
for various clients across the globe.
\item Working on various reusable UI components used in FusionCharts website to provide delightful and compelling user-centered experiences across all the interfaces. Also responsible for managing and organizing bug thrashing sessions to discuss and resolve bugs with other developers.
\item Making use of different developer tools to ensure front-end code and assets are optimized. 
\item Working on end-to-end development for FusionCharts core-product component themes.
\item Responsible for release process and smooth execution of new sprint or projects.
\end{tightemize}
\sectionsep

\runsubsection{Sr. Technical Specialist}
\descript{| FusionCharts }
\location{April 2017 - July 2018 | Bangalore, Karnataka, IN}
\vspace{\topsep}
\begin{tightemize}
\item Developed dashboards, POC’s and code samples for prospective and current clients using JavaScript, jQuery, PHP, MySQL, PostgreSQL, MongoDB, TaffyDB etc.
\item Worked with product management and development team to continuously evolve the product based on user feedback, reported issues and new technology trends.
\item Handled development of FusionMaps.
\end{tightemize}
\sectionsep

\runsubsection{Technical Specialist}
\descript{| FusionCharts }
\location{September 2015 - March 2017 | Bangalore, Karnataka, IN}
\vspace{\topsep}
\begin{tightemize}
\item Helped developers to integrate the product in their platforms by creating samples using different client side (JavaScript, jQuery) and server side (PHP) technologies.
\item Handled development of FusionMaps.
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RECENT PROJECTS: Part - 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects \& Experiments}
\runsubsection{Episteme} \custombold{//WIP}
\vspace{\topsep}
\begin{tightemize}
\item A no-nonsense knowledge aggregator for designers, developers and marketers etc.
\end{tightemize}
\sectionsep

\runsubsection{SaaS Dashboard}
\vspace{\topsep}
\begin{tightemize}
\item SaaS Dashboard from Google Sheets API to analyze different SaaS business metrics using React, FusionCharts and Bulma CSS framework.
\item Github repo: \href{http://bit.ly/react-gsheetsapi-saas-dashboard}{http://bit.ly/react-gsheetsapi-saas-dashboard}
\end{tightemize}
\sectionsep


\end{minipage} 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Page: 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth}

\vspace{\topsep}
\vspace{\topsep}
\vspace{\topsep}
\vspace{\topsep}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Passion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Passion}
Programming \\
Products \\
Reading \\
Playing Badminton \\
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Languages}
English \\
Hindi \\
\sectionsep



\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth}

\vspace{\topsep}
\vspace{\topsep}
\vspace{\topsep}
\vspace{\topsep}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RECENT PROJECTS: Part - 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\runsubsection{csv2table}
\vspace{\topsep}
\begin{tightemize}
\item Vanilla JavaScript component to generate HTML Table from CSV String.
\item Github repo: \href{http://bit.ly/sikrigagan-csv2table}{http://bit.ly/sikrigagan-csv2table}
\end{tightemize}
\sectionsep

\runsubsection{Smart Energy Monitoring Dashboard}
\vspace{\topsep}
\begin{tightemize}
\item Smart home dashboard using React, Redux (state management), FusionCharts and Bootstrap CSS framework to get visibility of energy consumption and costs for different appliances.
\item Link: \href{http://bit.ly/sikrigagan-energy-dashboard}{http://bit.ly/sikrigagan-energy-dashboard}
\end{tightemize}
\sectionsep

\runsubsection{LivSmart}
\vspace{\topsep}
\begin{tightemize}
\item Aadhaar Card based medical record and audit system with ability to provide collaboration for people with doctors, hospitals, blood banks, government and other international organisations.
\end{tightemize}
\sectionsep



\end{minipage}



\end{document}  \documentclass[]{article}
